Using CopyKAT to identify tumor cells in Ewing sarcoma samples

### 2024-06-12 analyses/cell-type-ewings/template_notebooks/03-copykat.Rmd
make sure copykat results are saved to proper location

# output classifications file 
copykat_results_file <- file.path(params$results_dir, glue::glue("{params$library_id}_copykat-classifications.tsv"))
```

>>>>

# output classifications file 
copykat_results_file <- file.path(params$results_dir, params$sample_id, glue::glue("{params$library_id}_copykat-classifications.tsv"))
```
